---
title: "W241 Final Project"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown



```{r}
# Load packages
library(foreign)
library(data.table)
library(knitr)
library(sandwich)
library(lmtest)
library(dplyr)
library(AER)
library(stargazer)
```


```{r}
# load the raw aggregated data downloaded from Facebook
d_raw <- fread("data_w241_final_project.csv")
d_raw <- as.data.frame(d_raw)
head(d_raw)
```

```{r}
# Transform the data by creating records from the aggregated records

ROW_COUNT = nrow(d_raw)
reivew_image = c()
postive_review = c()
ad = c()
platform = c()
click = c()

for (i in 1:ROW_COUNT) {
  ad_set <- d_raw[i,"Ad Set Name"]
  device_platform <- d_raw[i, "Device Platform"]
  reach <- d_raw[i, "Reach"]
  unique_clicks <- d_raw[i, "Unique Link Clicks"]
  
  if (ad_set == "Ad Set for Ad A") {
    reivew_image <- append(reivew_image, rep(1, reach))
    postive_review <- append(postive_review, rep(1, reach))
  } else if (ad_set == "Ad Set for Ad B") {
    reivew_image <- append(reivew_image, rep(0, reach))
    postive_review <- append(postive_review, rep(1, reach))
  } else if (ad_set == "Ad Set for Ad C") {
    reivew_image <- append(reivew_image, rep(1, reach))
    postive_review <- append(postive_review, rep(0, reach))
  } else {
    reivew_image <- append(reivew_image, rep(0, reach))
    postive_review <- append(postive_review, rep(0, reach))
  }
  
  platform <- append(platform, rep(device_platform, reach))
  
  click <- append(click, rep(1, unique_clicks))
  click <- append(click, rep(0, reach - unique_clicks))
}

d <- data.table(reivew_image = reivew_image,
                postive_review = postive_review,
                platform = platform,
                click = click)

# Look at data summary to confirm the number of data loaded and check means and quntiles
summary(d)
```


```{r}
mod_1 <- d[, lm(click ~ reivew_image + postive_review + reivew_image * postive_review)]
summary(mod_1)

# When negative review + WITHOUT PICTURE -> positive review + WITHOUT PICTIRE: the impact in click rate we expect (-0.0017)
```

```{r}
d[, negative_review := (postive_review - 1) * -1]
d[, no_image := (reivew_image - 1) * -1]

mod_2 <- d[, lm(click ~ no_image + negative_review + no_image * negative_review)]
summary(mod_2)

# The negative_review here means:
# When positve review + PICTURE -> negative review + picture: the impact in click rate we expect
# When positive review + WITHOUT PICTURE -> negative reivew + WITHOUT PICTURE: (-0.0058+0.0075=0.0017)
```

__Check the rubrics (both paper and presentation)__
1. think about what needs to be added to the presentation
2. think about any questions for the paper

Things to think about for analysis:
1. whether to use robust se
2. our plan and excution of HTEs

Things for discussion
1. potential interference from post sharing and comments
2. mediation discussion what really caused the difference
    a. the composition of the cards
    b. the potential issues from the smiling pictures
3. future work




```{r}
#data preparation
#d <- ('http://ischool.berkeley.edu/~d.alex.hughes/data/hill_kousser_analysisFile.csv')

# d <- data.frame("id" = 1:103126)
# 
# d$adgroup  = c(rep("Ad Set A", 23616),  rep("Ad Set B", 23496), rep("Ad Set C", 27230), rep("Ad Set D", 28784))
# 
# d$platform  = c(rep("mobile_app", 22272),  rep("mobile_web", 1072),rep("desktop", 272), 
#                 rep("mobile_app", 22032),  rep("mobile_web", 952),rep("desktop", 512),
#                 rep("mobile_app", 25600), rep("desktop", 934), rep("mobile_web", 696),
#                 rep("mobile_app", 25888), rep("desktop", 1856), rep("mobile_web", 1040))
# 
# 
# 
# d$uniqueclicks = c(rep(1, 569), rep(0, 22272 - 569), rep(1, 22), rep(0, 1072-22), rep(1,9), rep(0,272-9),
#                    rep(1, 320), rep(0, 22032 - 320), rep(1, 10), rep(0, 952-10), rep(1,3), rep(0,512-3),
#                    rep(1, 503), rep(0, 25600 - 503), rep(1, 16), rep(0, 934-16), rep(1,15), rep(0,696-15),
#                     rep(1, 419), rep(0, 25888 - 419), rep(1, 23), rep(0, 1856-23), rep(1,14), rep(0,1040-14))
# 
# 
# d$picture = c(rep(1,23616), rep(0, 23496), rep(1, 27230), rep(0,28784))
# 
# d$positive_rev = c(rep(1,47112), rep(0,56014))
# 
# head(d)



```



```{r}

# d2 <- data.table(d)
# d$nopicture = 1-d$picture
# d$negative_rev= 1-d$positive_rev
# 
# d2[]
# 
# mod1 = lm(uniqueclicks*100 ~ picture, data = d)
# summary(mod1)
# 
# 
# mod2 = lm(uniqueclicks*100 ~ picture + positive_rev, data = d)
# summary(mod2)
# 
# 
# mod3 = lm(uniqueclicks*100 ~ picture + positive_rev + picture * positive_rev, data = d)
# summary(mod3)
# 
# 
# 
# mod5 = lm(uniqueclicks*100 ~ nopicture+ negative_rev + negative_rev * nopicture, data = d)
# summary(mod5)
# 
# 
# modvar = vcovHC(mod5)
# 
# coeftest(mod5, modvar)

```
